Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-27 Markdown Documents/Manuscript.Rmd
small spacing change

# 2. Methods
```{r include=FALSE, cache=TRUE}
library(tidyverse)
library(lme4)
library(rstanarm)
library(rstan)
library(zoo)
library(formattable)
load("~/SmokeProject/ModelObjects/feefit.rda")
load("~/SmokeProject/ModelObjects/residuals.rda")
load("~/SmokeProject/ModelObjects/CVResidualMod.rds")
```
## 2.1. Data Collection

@@

@@

```{r echo=FALSE, cache=TRUE, message=FALSE,warning=FALSE, fig.height = 9, fig.width = 12}
pars+ggplot2::ggtitle("Posterior medians with 50% and 90% intervals")+
  ggplot2::scale_y_discrete(name ="Park",labels=rev(PNames),limits=rev(limits))+
  mytheme+scale_x_continuous(name="Parameter Value", labels = scales::comma)+
  theme(panel.grid.major.y = element_line(color = "lightgrey", linetype="dotted")) 
```

>>>>

# 2. Methods
```{r include=FALSE, cache=TRUE}
library(tidyverse)
library(lme4)
library(rstanarm)
library(rstan)
library(zoo)
library(formattable)
load("~/SmokeProject/ModelObjects/feefit.rda")
load("~/SmokeProject/ModelObjects/residuals.rda")
load("~/SmokeProject/ModelObjects/CVResidualMod.rds")
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```
## 2.1. Data Collection

@@

<!-- This is how you comment -->

@@

```{r echo=FALSE, cache=TRUE, message=FALSE,warning=FALSE, fig.height = 9, fig.width = 12}
pars+ggplot2::ggtitle("Posterior medians with 50% and 90% intervals")+
  ggplot2::scale_y_discrete(name ="Park",labels=rev(PNames),limits=rev(limits))+theme_classic()+
  mytheme+scale_x_continuous(name="Parameter Value", labels = scales::comma)+
  theme(panel.grid.major.y = element_line(color = "lightgrey", linetype="dotted")) 
```
